---
title: "MC_SMCVAS Baseline Analysis"
author: "AbdulHafiz Abba"
date: "2025-06-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(readxl)

df <- read_excel("Dataset/SMC_VAS BAUCHI BASELINE SURVEY 2025_Play.xlsx")
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

```
```{r echo=FALSE, warning=FALSE}
# Calculate frequency and percent
lga_table <- as.data.frame(table(df$LGA))
colnames(lga_table) <- c("LGA", "Frequency")

# Calculate percentages
lga_table$Percent <- round((lga_table$Frequency / sum(lga_table$Frequency)) * 100, 1)

# Add total row
total_row <- data.frame(
  LGA = "Total",
  Frequency = sum(lga_table$Frequency),
  Percent = 100.0
)

# Combine
lga_table_final <- rbind(lga_table, total_row)

# Print the result
print(lga_table_final, row.names = FALSE)
```
```{r echo=FALSE}
# Load required libraries


# Replace with your actual data import
# df <- read.csv("your_data.csv")

# Summarize LGA frequencies
lga_table <- df %>%
  count(LGA) %>%
  arrange(LGA)  # alphabetical sort

# Plot bar chart sorted alphabetically
ggplot(lga_table, aes(x = LGA, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = n), vjust = -0.5, size = 3.5) +
  labs(title = "Distribution of Respondents by LGA",
       x = "LGA",
       y = "Frequency") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


## Analyze Relationships of the Wealth Index With Other Key Variables

### Creating the Coverage Variables

```{r}
df <- df %>%
  mutate(
    VAS_coverage = ifelse(`Did [selected_chi_name] received vitamin A dose within the last 6 months from any source?` == "Yes", 1, 0),
    Deworming_coverage = ifelse(`Did [selected_chi_name] receive a deworming tablet (during the last MNCHW campaign) from any source?` == "Yes", 1, 0),
    MUAC_coverage = ifelse(`Did [selected_chi_name] received a MUAC screening (during the last MNCHW campaign) from any source?` == "Yes", 1, 0),
    Immunization_coverage = ifelse(`Question: Did [selected_chi_name] receive any vaccine during the last MNCHW campaign?` == "Yes", 1, 0)

  )

```

```{r}

coverage_services <- df %>%
  group_by(LGA) %>%
  summarize(
    VAS = mean(VAS_coverage, na.rm = TRUE),
    Deworming = mean(Deworming_coverage, na.rm = TRUE),
    MUAC = mean(MUAC_coverage, na.rm = TRUE),
    Immunization = mean(Immunization_coverage, na.rm = TRUE),
    n = n()
  )

print(coverage_services)


```
##  Coverage of Key Child Health Interventions Across LGAs


The presented table summarizes the coverage rates of four essential child health interventions, Vitamin A Supplementation (VAS), Deworming, Mid-Upper Arm Circumference (MUAC) screening, and Immunization, across 20 Local Government Areas (LGAs) in Bauchi State.

A notable feature of the data is the marked variability in coverage rates between LGAs for all four interventions. Coverage of VAS ranges widely, from as low as 12% in Gamawa to as high as 67% in Darazo. Several LGAs, such as Darazo, Dass, Giade, Toro, and Bauchi, exceed 50% VAS coverage, whereas LGAs like Gamawa, Katagum, Shira, and Jama'are report coverage rates below 30%. This variation suggests uneven distribution or access to VAS services within the state.

Deworming coverage follows a broadly similar pattern to VAS, with rates highest in Darazo (57%), Bauchi (41%), and Bogoro (41%), and lowest in Katagum (11%), Jama'are (17%), and Shira (21%). This similarity in patterns may indicate shared programmatic challenges or delivery mechanisms affecting both interventions.

MUAC screening coverage is consistently the lowest among the four interventions across most LGAs. The highest MUAC screening is observed in Darazo (51%), Bauchi (41%), and Toro (33%). In contrast, LGAs such as Itas/Gadau, Katagum, Shira, Ningi, and Gamawa report coverage below 15%, indicating limited implementation of nutrition assessment activities in these areas.

Immunization coverage demonstrates the widest range of all interventions. Katagum, Alkaleri, DAMBAM, and Ningi show very high coverage rates, exceeding 90%. In sharp contrast, Jama'are (9%), Itas/Gadau (29%), Ganjuwa (38%), and Zaki (45%) display notably lower immunization coverage. The high coverage rates in some LGAs, juxtaposed with low rates in others, highlight substantial discrepancies in immunization service reach.

Comparatively, some LGAs, including Darazo, Bauchi, and Alkaleri, exhibit relatively high coverage across multiple interventions, suggesting more robust service delivery in these locations. Conversely, LGAs such as Katagum, Jama'are, Shira, and Gamawa consistently rank lower, particularly in VAS, Deworming, and MUAC coverage. Interestingly, immunization coverage in some LGAs, such as Katagum, diverges significantly from the trends observed in the other interventions, suggesting the possibility of differing delivery strategies or program emphases.



```{r}
# Table of Coverage by LGA and Service for Plotting
coverage_long <- coverage_services %>%
  pivot_longer(
    cols = c(VAS, Deworming, MUAC, Immunization),
    names_to = "Service",
    values_to = "Coverage"
  )

# Visualize Coverage by LGA and Service
ggplot(coverage_long, aes(x = LGA, y = Coverage, fill = Service)) +
  geom_col(position = position_dodge(width = 0.9)) +
  geom_text(
    aes(label = scales::percent(Coverage, accuracy = 1)),
    position = position_dodge(width = 0.9),
    vjust = -0.3,
    size = 3
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.1))) +
  labs(
    title = "Coverage of VAS, Deworming, MUAC, and Immunization by LGA",
    x = "LGA",
    y = "Coverage (%)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))


```
##  Statistical Test for Difference in Coverage Across LGAs

Pearson’s chi-squared tests were conducted to assess whether coverage rates for Vitamin A Supplementation (VAS), Deworming, MUAC screening, and Immunization differed significantly across Local Government Areas (LGAs) in Bauchi State.

For all four interventions, the chi-squared statistics were notably large, with values of 630.91 for VAS (df = 19), 402.38 for Deworming (df = 19), 624.52 for MUAC screening (df = 19), and 138.08 for Immunization (df = 19). In each case, the associated p-value was less than 2.2e-16.

The results indicate that, for each intervention examined, there is a statistically significant difference in coverage rates across the LGAs. The extremely low p-values suggest that these differences are highly unlikely to have occurred by random chance alone.

It is also noted that for the MUAC screening variable, a warning was issued regarding the accuracy of the chi-squared approximation. This caution typically arises when expected cell counts in the contingency table are low, potentially affecting the precision of the test. Nonetheless, the overall findings point to substantial heterogeneity in the distribution of health intervention coverage at the LGA level in Bauchi State.


```{r}
# VAS
chisq_vas <- chisq.test(table(df$LGA, df$VAS_coverage))
print(chisq_vas)

# Deworming
chisq_deworming <- chisq.test(table(df$LGA, df$Deworming_coverage))
print(chisq_deworming)

# MUAC
chisq_muac <- chisq.test(table(df$LGA, df$MUAC_coverage))
print(chisq_muac)

# Immunization
chisq_immun <- chisq.test(table(df$LGA, df$Immunization_coverage))
print(chisq_immun)

```



## Wealth Index Analysis

```{r}

df <- df %>%
  mutate(
    water_source_score = case_when(
      HH_watersource == "Piped water" ~ 3,
      HH_watersource == "Bottled water" ~ 5,
      HH_watersource == "Sachet water/pure water" ~ 4,
      HH_watersource == "Rainwater" ~ 0,
      HH_watersource == "Tanker truck" ~ 1,
      HH_watersource == "Cart with small tank" ~ 0,
      HH_watersource == "Dug well" ~ 0,
      HH_watersource == "Surface water (river/dam/lake/pond/stream/canal/irrigation channel)" ~ 0,
      HH_watersource == "Others" ~ 0,
      HH_watersource == "" | is.na(HH_watersource) ~ 0,
      HH_watersource == "Water from spring" ~ 0,
      TRUE ~ 0
    ),
    toilet_type_score = case_when(
      HH_Toilet_type == "FLUSH OR POUR FLUSH TOILET" ~ 3,
      HH_Toilet_type == "PIT LATRINE" ~ 1,
      HH_Toilet_type == "" | is.na(HH_Toilet_type) ~ 0,
      TRUE ~ 0
    ),
    electricity_score = ifelse(HH_appliance_Electricity == "Yes", 1, 0),
    refrigerator_score = ifelse(HH_appliance_Refregerator == "Yes", 1, 0),
    radio_score = ifelse(HH_appliance_Radio == "Yes", 1, 0),
    TV_score = ifelse(HH_appliance_Television == "Yes", 1, 0),
    cable_TV_score = ifelse(HH_appliance_Cable_TV == "Yes", 1, 0),
    AC_score = ifelse(HH_appliance_Air_Conditioner == "Yes", 1, 0),
    computer_score = ifelse(HH_appliance_Computer == "Yes", 1, 0),
    fan_score = ifelse(HH_appliance_Fan == "Yes", 1, 0),
    non_appliance_score = ifelse(HH_appliance_None == "Yes", 1, 0),
    iron_score = ifelse(`HH_appliance_Electronic Iron` == "Yes", 1, 0),
    generating_set_score = ifelse(`HH_appliance_Generating Set` == "Yes", 1, 0),
    mobile_Phone_score = ifelse(`HH_appliance_Mobile telephone` == "Yes", 1, 0),
    non_mobile_phone_score = ifelse(`HH_appliance_Non_Mobile telephone` == "Yes", 1, 0),
    floor_type_score = case_when(
      HH_floor_type == "FINISHED FLOOR" ~ 3,
      HH_floor_type == "NATURAL FLOOR" ~ 0,
      TRUE ~ 0
    ),
    fuel_source_score = case_when(
      HH_fuel_source == "ELECTRICITY" ~ 5,
      HH_fuel_source == "AGRICULTURAL CROP" ~ 0,
      HH_fuel_source == "ANIMAL DUNG" ~ 0,
      HH_fuel_source == "BIOGAS" ~ 3,
      HH_fuel_source == "CHARCOAL" ~ 2,
      HH_fuel_source == "COAL, LIGNITE" ~ 2,
      HH_fuel_source == "LIQUID PROPANE GAS/CYLINDER" ~ 4,
      HH_fuel_source == "NATURAL GAS" ~ 4,
      HH_fuel_source == "STRAW/SHRUBS/GRASS/SAWDUST" ~ 1,
      HH_fuel_source == "WOOD" ~ 1,
      HH_fuel_source == "" | is.na(HH_fuel_source) ~ 0,
      TRUE ~ 0
    )
  )

```
```{r}
df <- df %>%
  mutate(
    wealth_score = rowSums(
      across(
        c(
          water_source_score,
          toilet_type_score,
          electricity_score,
          refrigerator_score,
          radio_score,
          TV_score,
          cable_TV_score,
          AC_score,
          computer_score,
          fan_score,
          non_appliance_score,
          iron_score,
          generating_set_score,
          mobile_Phone_score,
          non_mobile_phone_score,
          floor_type_score,
          fuel_source_score
        )
      ),
      na.rm = TRUE
    )
  )


```
## Summarize the Wealth Score Distribution
```{r}
summary(df$wealth_score)
hist(df$wealth_score)
boxplot(df$wealth_score)

df <- df %>%
  mutate(
    wealth_quintile = ntile(wealth_score, 5),
    wealth_quintile_label = factor(
      wealth_quintile,
      levels = 1:5,
      labels = c("Poorest", "Poor", "Middle", "Rich", "Richest")
    )
  )



```


## Compare Coverage by Wealth Quintile
```{r}
library(janitor)
df %>%
  tabyl(wealth_quintile_label, VAS_coverage) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting()

```
## Barplot of VAS coverage by wealth:
```{r}
library(ggplot2)
df %>%
  group_by(wealth_quintile_label) %>%
  summarize(VAS_coverage_rate = mean(VAS_coverage, na.rm = TRUE)) %>%
  ggplot(aes(x = wealth_quintile_label, y = VAS_coverage_rate, fill = wealth_quintile_label)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "VAS Coverage by Wealth Quintile", x = "Wealth Quintile", y = "Coverage (%)") +
  theme_minimal() +
  theme(legend.position = "none")

```



